---
title: "Assignment_Module 8_DEA"
author: "Venkata Naga Siddartha Gutha"

output:
  pdf_document: default
  html_document: default
---

```{r}
knitr::opts_chunk$set(message = FALSE)
knitr::opts_chunk$set(warning = FALSE)
```

```{r}
library("Benchmarking")

table_values <- matrix(c("Facility 1","Facility 2","Facility 3","Facility 4",
                         "Facility 5", "Facility 6",
                150,400,320,520,350,320,
                0.2,0.7,1.2,2.0,1.2,0.7,
                14000,14000,42000,28000,19000,14000,
                3500,21000,10500,42000,25000,15000), ncol=5, byrow=F)

colnames(table_values) <- c("DMU", "Staff_Hours_Per_Day","Supplies_Per_Day",
                            "Reimbursed_Patient_Days","Privately_Paid_Patient_Days")

table <- as.table(table_values)
table_values
```
**calculating Constant that Returns to Scale (CRS)**
```{r}
x <- matrix(c(150,400,320,520,350,320,
            0.2,0.7,1.2,2.0,1.2,0.7),ncol=2)

y <- matrix(c(14000,14000,42000,28000,19000,14000,
                3500,21000,10500,42000,25000,15000),ncol=2)

colnames(x) <- c("Staff_Hours_Per_Day","Supplies_Per_Day")

colnames(y) <- c("Reimbursed_Patient_Days","Privately_Paid_Patient_Days")


D_E_A_crs<-dea(x, y, RTS = "crs")
D_E_A_crs

peers(D_E_A_crs)
lambda(D_E_A_crs)
```
**CRS Observations:-**

a. From the above output it can be seen that Facility 1, Facility 2, Facility 3  and Facility 4 are efficient.

b. Facility 1, Facility 2 and Facility 4 are the peer members for Facility 5 and Facility 6 which are the inefficient facilities.

c. Facility 5 is 97.75 % efficient leaving 2.25 % as inefficient 

d. Facility 6 is 86.75 % efficient leaving 13.25 % as inefficient.


**Calculating the Decreasing that returns to Scale (DRS)**
```{r}
D_E_A_drs <- dea(x, y, RTS = "drs")
D_E_A_drs


peers(D_E_A_drs)
lambda(D_E_A_drs)
```
**DRS Observations** 

1. Facility 1, Facility 2, Facility 3  and Facility 4 are efficient.

2. Facility 1, Facility 2 and Facility 4 are the peer members for Facility 5 and Facility 6 which are inefficient facilities.

3. Facility 5 is 97.75 % efficient leaving 2.25 % as inefficient 

4. Facility 6 is 86.75 % efficient leaving 13.25 % as inefficient.



**Calculating Increasing Returns to Scale (IRS)**
```{r}
D_E_A_irs <- dea(x, y, RTS = "irs")
D_E_A_irs

peers(D_E_A_irs)
lambda(D_E_A_irs)
```
*IRS Observations*

1. Facility 1, Facility 2, Facility 3, Facility 4 and Facility 5 are efficient.

2. Facility 1, Facility 2 and Facility 5 are the peer members for Facility 6 which is inefficient facility.

3. Facility 6 is 89.63 % efficient leaving 10.37 % as inefficient.

*Calculating Variable Returns to Scale (VRS)*
```{r}
D_E_A_vrs <- dea(x, y, RTS = "vrs")
D_E_A_vrs

peers(D_E_A_vrs)
lambda(D_E_A_vrs)
```
*VRS Observations* 

1. Facility 1, Facility 2, Facility 3, Facility 4 and Facility 5 are efficient.

2. Facility 1, Facility 2 and Facility 5 are the peer members for Facility 6 which is the only inefficient facility.

3. Facility 6 is 89.63 % efficient leaving 10.37 % as inefficient.

*Calculating the Free Disposability Hull (FDH)*
```{r}
D_E_A_fdh <- dea(x, y, RTS = "fdh")
D_E_A_fdh

peers(D_E_A_fdh)
lambda(D_E_A_fdh)
```
*FDH Observations * 

All the DMUs are efficient this is due to the principal which FDH technique follows.

*Calculating Free Replicability Hull (FRH)*
```{r}
#Here FRH is calculated by specifying RTS = "add"
D_E_A_frh <- dea(x, y, RTS = "add")
D_E_A_frh

peers(D_E_A_frh)
lambda(D_E_A_frh)
```
*FRH Observations * 

All the DMUs are efficient. It follows the no convexity assumption it  ensures that the o/p is free from disposal and replication.


*Summary of Results (Inefficient DMUs)*
```{r}
summary_Inefficient_DMUs <- matrix(c("CRS","DRS","IRS","VRS","FDH","FRH",
2,2,1,1,0,0,
"Facility 5 & 6", "Facility 5 & 6","Facility 6", "Facility 6", "-","-",
"97.75% & 86.7%","97.75% & 86.7%","89.63%","89.63%","-","-",
"Facility 1, 2 & 4","Facility 1, 2 & 4","Facility 1, 2 & 5",
"Facility 1, 2 & 5","-","-","0.2, 0.08, 0.54 and 0.34, 0.4, 0.13", "0.2, 0.08, 
0.54 and 0.34, 0.4, 0.13", "0.4, 0.34 and 0.26", "0.4, 0.34 and 0.26", "-","-"),
ncol=6,byrow=F)


colnames(summary_Inefficient_DMUs) <- c("RTS","Count_Inefficient_DMUs",
                                        "Name_DMUs","%_Inefficiency",
                                        "Peers","Lambda")

as.table(summary_Inefficient_DMUs)
```


*Summary of Results (Efficient DMUs)*
```{r}
summary_Inefficient_DMUs<- matrix(c("CRS","DRS","IRS","VRS","FDH","FRH",
"Facility 1, 2, 3 & 4","Facility 1, 2, 3 & 4","Facility 1, 2, 3, 4 & 5", 
"Facility 1, 2, 3, 4 & 5", "All DMUs", "All DMUs"), ncol = 2, byrow=F)

colnames(summary_Inefficient_DMUs) <- c("RTS", "Efficient_DMUs")

as.table(summary_Inefficient_DMUs)
```
*Interpretation of the DEA Analysis  *

Constant Returns to Scale (CRS) is regarded as the original scale and is utilized by the majority of businesses.The Free Disposability and Free Replicability Hull (FDH & FRH), which makes no assumptions about convexity, is regarded as a non-parametric way to evaluate the effectiveness of DMUs.The dispersion scales known as Decreasing, Increasing and Varying Returns to Scale (DRS, IRS, and VRS) aid us in determining what to increase and what to decrease based on the deployment of information.

CRS - Constant Returns to Scale

DMUs 1, 2, 3 and 4 are efficient. DMU(5) is only 97.75% efficient, and DMU(6) is 86.7% efficient. the peer units for DMU(4) are 1, 2 and 4 with relative weights of 0.2, 0.08 and 0.54.The peer units OF DMU(6) are 1, 2 and 4 with weights of 0.34, 0.4 and 0.13 respectively.CRS helps us to know if any possible DMUs can be scaled up or down. Here DMUs 1, 2, 3 and 4 can be scaled up.

DRS - Decreasing Returns to Scale

DMUs 1, 2, 3 and 4 are efficient. DMU(5) is only 97.75% efficient and DMU(6) is 86.7% efficient. the peer units for DMU(4) are 1, 2 and 4 with relative weights of 0.2, 0.08 and 0.54. Similarly for DMU(6), the peer units are 1, 2 and 4 with weights of 0.34, 0.4 and 0.13 respectively. In this case DMU 5 & 6 can be scaled down.

IRS - Increasing Returns to Scale
DMUs 1, 2, 3, 4 and 5 are efficient. DMU(6) is only 89.63% efficient. the peer units for DMU(6) are 1, 2 and 5 with relative weights of 0.4, 0.34 and 0.26 respectively. IRS helps in increasing the scale of operation by looking at the efficiency scores

VRS - Variable Returns to Scale

DMUs 1, 2, 3, 4 and 5 are efficient. DMU(6) is only 89.63% efficient. the peer units for DMU(6) are 1, 2 and 5 with relative weights of 0.4, 0.34 and 0.26 respectively. VRS provides idea on increasing or decreasing the scale of operations with variations towards the input and output factor.


FDH - Free Disposability Hull

The results indicate that all the DMUs are efficient. This is because there is no convexity assumption 

FRH - Free Replicability Hull

The results indicate that all the DMUs are efficient. This is because there is no convexity assumption




*Plotting the Graphs*

*CRS Plot*
```{r}
dea.plot(x, y, RTS='crs')
```

*DRS Plot*
```{r}
dea.plot(x,y,RTS="vrs") 
```

*IRS Plot*
```{r}
dea.plot(x,y,RTS="irs")
```

*VRS Plot*
```{r}
dea.plot(x,y,RTS="vrs")
#tinytex::install_tinytex()

```

*FDH Plot*
```{r}
dea.plot(x,y,RTS="fdh")
```

*FRH Plot*
```{r}
dea.plot(x,y,RTS="add")
```


