---
title: "Assignment:Module 11"
author: "Venkata Naga Siddartha Gutha"
date: "`r Sys.Date()`"
output: pdf_document
---

```{r}
library(lpSolveAPI)
Model_AP<-read.lp("C:/Users/sidda/Desktop/KSU_Fall/QMM/Assignemnt module 11/qmm.lp")
Model_AP
```

```{r}
solve(Model_AP)

```
Here 0 indicates that the model exists

```{r}
get.objective(Model_AP)

```
To ensure that there are enough number of workers available on each day with the given wages it costs the company $25,675.
```{r}

get.variables(Model_AP)
```
x1= Employees on Shift 1=2
\newline
x2= Employees on Shift 2=4
\newline
x3= Employees on Shift 3=5
\newline
x4= Employees on Shift 4=0
\newline
x5= Employees on Shift 5=8
\newline
x6= Employees on Shift 6=1
\newline
x7= Employees on Shift 7=13
\newline


Therefore Number of employees working on each day are as follows:
\newline
Sunday: x2 + x3 + x4 + x5 + x6 = 18
\newline
Monday: x3 + x4 + x5 + x6 + x7 = 27
\newline
Tuesday: x4 + x5 + x6 + x7 + x1 = 24
\newline
Wednesday: x5 + x6 + x7 + x1 + x2 = 28
\newline
Thursday: x6 + x7 + x1 + x2 + x3 = 25
\newline
Friday: x7 + x1 + x2 + x3 + x4 = 24
\newline
Saturday: x1 + x2 + x3 + x4 + x5 = 19
\newline



